class: center, middle, inverse

# `r icon::fa("chart-line", size = 1)` `r icon::fa("chart-pie", size = 1)` `r icon::fa("chart-area", size = 1)` <br> Data Visualization 

---
## Mortality rate

```{r, echo=FALSE}
htmltools::img(src = "img/logo-mg.png", 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:15%')
```

- The blue lines indicate the dates that SAMU consortiums were implemented.
- The rate was age-standardized (adjusted) by MG population in 2010.

```{r mg-bh, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=10/1.618, fig.width=10,dpi = 300}
mg <- readRDS("../data/mg_rate.rds")
consorcio_df <- readRDS("../data/consorcio.rds") %>%
  mutate(DATA_IMPLEMENTACAO = as.Date(DATA_IMPLEMENTACAO)) %>%
  filter(lubridate::year(DATA_IMPLEMENTACAO) > 2008)

gg_mortalidade <- ggplot(data = mg, aes(x = DATA, y = 1e5*TAXA_MORTALIDADE)) +
  geom_vline(data = consorcio_df,  aes(xintercept = DATA_IMPLEMENTACAO), color = "steelblue", size = 1) +
  geom_point(color = verde_ts, size = 2) +
  geom_line(color = verde_ts, size = 1) +
  geom_smooth(method = 'loess', color = "indianred2", size = 1) +
  labs(y = "Mortality rate for 100.000", x = "") +
  theme_minimal() +
  theme(axis.text = element_text(size = 18),
        axis.title = element_text(size = 18, face="bold"))

gg_internacao <- ggplot(data = mg, aes(x = DATA, y = 1e5*TAXA_INTERNACAO)) +
    geom_vline(data = consorcio_df,  aes(xintercept = DATA_IMPLEMENTACAO), color = "steelblue", size = 1) +
  geom_point(color = verde_ts, size = 2) +
  geom_line(color = verde_ts, size = 1) +
  geom_smooth(method = 'loess', color = "indianred2", size = 1) +
  labs(y = "Hospitalization rate per 100.000", x = "") +
  theme_minimal() +
  theme(axis.text = element_text(size = 18),
        axis.title = element_text(size = 18, face="bold"))

gg_letalidade <- ggplot(data = mg, aes(x = DATA, y = TAXA_LETALIDADE)) +
    geom_vline(data = consorcio_df,  aes(xintercept = DATA_IMPLEMENTACAO), color = "steelblue", size = 1) +
  geom_point(color = verde_ts, size = 2) +
  geom_line(color = verde_ts, size = 1) +
  geom_smooth(method = 'loess', color = "indianred2", size = 1) +
  scale_y_continuous(labels = percent) + 
  labs(y = "Hospitalization rate for 100.000", x = "") +
  theme_minimal() +
  theme(axis.text = element_text(size = 18),
        axis.title = element_text(size = 18, face="bold"))
gg_mortalidade
```

---
## Lethality rate

```{r, echo=FALSE}
htmltools::img(src = "img/logo-mg.png", 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:15%')
```

- The blue lines indicate the dates that SAMU consortiums were implemented.
- The rate was age standardized (adjusted) by MG hospitalization in 2010.

```{r mg-letalidade, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=10/1.618, fig.width=10,dpi = 300}
gg_letalidade
```

---
## Hospitalization rate

```{r, echo=FALSE}
htmltools::img(src = "img/logo-mg.png", 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:15%')
```

- The blue lines indicate the dates that SAMU consortiums were implemented.
- The rate was age-standardized (adjusted) by MG hospitalization in 2010.

```{r mg-internacao, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=10/1.618, fig.width=10,dpi = 300}
gg_internacao
```

---
## Consortiums distribuition

```{r, echo=FALSE}
htmltools::img(src = "img/logo-mg.png", 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:15%')
```

<center>
<div class="divborder">
```{r mapa_consorcio, echo=FALSE, message=FALSE, warning=FALSE, child='mapa-consorcio.Rmd', out.width='100%'}
```
</div>
</center>

